---
title: "My silly report"
author: "Martha Clark"
date: "6/24/2021"
output: html_document
bibliography: bibliography.bib
---

```{r, include=FALSE, echo = TRUE, eval = TRUE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE)
```


```{r}
library(dplyr)
smoke <- c(TRUE, TRUE, TRUE, TRUE, TRUE, 
           TRUE, FALSE, TRUE, FALSE, FALSE, 
           FALSE, FALSE, FALSE, FALSE, FALSE, 
           FALSE, FALSE, TRUE, TRUE)
age <- c(35, 21, 20, 48, 20, 
         20, 22, 19, 19, 20, 
         19, 18, 24, 22, 22, 
         19, 21, 19, 21)
people <- data.frame(smoke, age)
people <- people %>%
  filter(age <= 34)

obs <- nrow(people)
```

# Introduction 

## Background

### Smoking: is it good for you?

Everyone knows that smoking is bad for you and math is easy [@Rudd2014].
Doctors shouldn't drink [@Peterman2005].

#### How many people smoke?

Lots

# Methods

My esteemed colleagues and I surveyed `r obs` people. The average age of them was `r round(mean(people$age))` years. That is very _young_. **RIGHT**

# **Results**
The below chart shows the age of participants.

```{r}
library(ggplot2)
ggplot(data = people,
       aes(x = age,
           y = smoke)) +
  geom_boxplot(fill = 'blue') 
```

# Conclusion

Some have smoked

# Bibliography